Extended Data

### 2021-11-16 doc/manuscript/Dow_Extended_Data.Rmd
further improve EDF 6-7
@camerondow35 , I think the extended data is good now, just need to address issues #90 , #88

###~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## some stats/ 
species_table <- read.csv(file = "tables_figures/species_table.csv")
n_dendro_trees <- sum(na.omit(species_table[, "n.trees"]))
n_dendro_trees_SCBI <- 123 #doing this the lazy way. summed from species_table rather than coded. 
n_dendro_trees_HF <- 340 #doing this the lazy way. summed from species_table rather than coded. 
n_tree_years <- sum(na.omit(species_table[, "n.tree.years"]))
n_cores_focal_sites <- sum(na.omit(species_table[, "n.cores"]))
chronology_table <- read.csv(file = "tables_figures/chronology_table.csv")
n_chronologies <- nrow(chronology_table)  
n_cores_sites <- length(unique(chronology_table[, "Location"]))
n_cores_species <- length(unique(chronology_table[, "Species"]))
n_chronologies_SCBI <- 12
n_chronologies_HF <- 4
```

@@

![**Extended Data Figure 7 | Sensitivity of annual growth, as derived from tree-rings, to monthly mean maximum temperatures ($T_{max}$) of the current and past year, for `r n_chronologies` chronologies from `r n_cores_sites` sites across eastern North America** (`r EDF_map `). Colors indicate the correlation between monthly $T_{max}$ and a dimensionless ring width index (RWI) derived from the multiple trees that form each chronology and emphasizing interannual variability associated with climate. Chronologies are grouped by xylem porosity and ordered by mean April $T_{max}$. Plots are annotated to highlight records from our two focal sites, the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest (HF) (`r EDT_species`). Figure presents the same results as main manuscript Fig. `r tree_rings` but extends back to include the previous year. Species analyzed and numbers of significant correlations to $T_{max}$ are summarized in `r EDT_tree_ring_summary`, and chronology details are given in `r chron_table`.](tables_figures/tree_rings_tmax_extended.png){ width=90% }

>>>>

###~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## some stats/ 
chronology_table <- read.csv(file = "tables_figures/chronology_table.csv")
n_chronologies <- nrow(chronology_table)  
n_cores_sites <- length(unique(chronology_table[, "Location"]))
n_cores_species <- length(unique(chronology_table[, "Species"]))

```

@@

![**Extended Data Figure 7 | Sensitivity of annual growth, as derived from tree-rings, to monthly mean maximum temperatures ($T_{max}$) of the current and past year, for `r n_chronologies` chronologies from `r n_cores_sites` sites across eastern North America** (`r EDF_map `). Colors indicate the correlation between monthly $T_{max}$ and a dimensionless ring width index (RWI) derived from the multiple trees that form each chronology and emphasizing interannual variability associated with climate. Chronologies are grouped by xylem porosity and ordered by mean April $T_{max}$. Plots are annotated to highlight records from our two focal sites, the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest (HF) (`r EDT_species`). Figure presents the same results as main manuscript Fig. 3 but extends back to include the previous year. Species analyzed and numbers of significant correlations to $T_{max}$ are summarized in `r EDT_tree_ring_summary`, and chronology details are given in `r chron_table`.](tables_figures/tree_rings_tmax_extended.png){ width=90% }
